---
title: "INTIS (INTENT Insights)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: spacelab
---

<style>
body {
    font-size: 14px;
}
</style>

```{r setup, include=FALSE}
# Load the necessary packages
pacman::p_load(tidyverse, flexdashboard, shiny, readxl, tmap, DT, leaflet)
data("World")

# Function for wrangling the Excel file
vol_df <- function(df, year, vol) {
  df_out <- df %>%
    group_by(Year, Volume) %>%
    filter(Year == year && Volume == vol)
  df_out <- rbind(
    cbind(df_out$Artist1, df_out$Country1),
    cbind(df_out$Artist2, df_out$Country2),
    cbind(df_out$Artist3, df_out$Country3),
    cbind(df_out$Artist4, df_out$Country4),
    cbind(df_out$Artist5, df_out$Country5),
    cbind(df_out$Artist6, df_out$Country6),
    cbind(df_out$Artist7, df_out$Country7)
  ) %>%
    na.omit() %>%
    as.data.frame()
  colnames(df_out) <- c("Artist", "Country")
  return(df_out)
}

# Function for forming links
createLink <- function(val) {
  val1 <- gsub(" ", "+", val)
  sprintf('<a href="https://www.google.com/search?as_epq=%s" target="_blank">%s</a>', val1, val)
}

# Function for mode
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

# Load the file
df <- read_excel("INTIS.xlsx")

# Prepare data for INTENT 2020
v2020_1 <- vol_df(df, 2020, 1)
v2020_2 <- vol_df(df, 2020, 2)
v2020_3 <- vol_df(df, 2020, 3)
v2020 <- rbind(v2020_1, v2020_2, v2020_3) %>% as.data.frame()
v2020_artists <- unique(v2020$Artist)
v2020_country <- table(v2020$Country) %>% as.data.frame()

# Prepare data for INTENT 2021
v2021_1 <- vol_df(df, 2021, 1)
v2021_2 <- vol_df(df, 2021, 2)
v2021_3 <- vol_df(df, 2021, 3)
v2021_4 <- vol_df(df, 2021, 4)
v2021_5 <- vol_df(df, 2021, 5)
v2021_6 <- vol_df(df, 2021, 6)
v2021 <- rbind(v2021_1, v2021_2, v2021_3, v2021_4, v2021_5, v2021_6) %>% as.data.frame()
v2021_artists <- unique(v2021$Artist)
v2021_country <- table(v2021$Country) %>% as.data.frame()

# Prepare data for INTENT 2022
v2022_1 <- vol_df(df, 2022, 1)
v2022_2 <- vol_df(df, 2022, 2)
v2022_3 <- vol_df(df, 2022, 3)
v2022_4 <- vol_df(df, 2022, 4)
v2022_5 <- vol_df(df, 2022, 5)
v2022_6 <- vol_df(df, 2022, 6)
v2022 <- rbind(v2022_1, v2022_2, v2022_3, v2022_4, v2022_5, v2022_6) %>% as.data.frame()
v2022_artists <- unique(v2022$Artist)
v2022_country <- table(v2022$Country) %>% as.data.frame()

# Prepare data for INTENT 2023
v2023_1 <- vol_df(df, 2023, 1)
v2023_2 <- vol_df(df, 2023, 2)
v2023_3 <- vol_df(df, 2023, 3)
v2023_4 <- vol_df(df, 2023, 4)
v2023_5 <- vol_df(df, 2023, 5)
v2023_6 <- vol_df(df, 2023, 6)
v2023_7 <- vol_df(df, 2023, 7)
v2023_8 <- vol_df(df, 2023, 8)
v2023_9 <- vol_df(df, 2023, 9)
v2023_10 <- vol_df(df, 2023, 10)
v2023 <- rbind(v2023_1, v2023_2, v2023_3, v2023_4, v2023_5, v2023_6,
               v2023_7, v2023_8, v2023_9, v2023_10) %>% as.data.frame()
v2023_artists <- unique(v2023$Artist)
v2023_country <- table(v2023$Country) %>% as.data.frame()

```

# Overview

## Column {data-width="650"}

### Contributing Countries

```{r}
# Prepare data for overview
v_artists <- c(v2020_artists, v2021_artists, v2022_artists, v2023_artists) %>%
  unique() %>%
  sort()
v_total <- rbind(v2020, v2021, v2022, v2023) %>% as.data.frame()
v_country <- table(v_total$Country) %>% as.data.frame()
colnames(v_country) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries <- inner_join(World, v_country, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries)) {
  v_t <- v_total %>%
    filter(Country == as.character(ContributingCountries$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))

```

## Row {data-width=180}

### Total Contributions

```{r}
# Show total contributions
valueBox(value = nrow(v_total), icon = "fa-music",
         caption = "Contributions", color = "darkseagreen")

```

### Total Artists

```{r}
# Show total artists
valueBox(value = nrow(v_artists %>% as.data.frame()), icon = "fa-users",
         caption = "Artists", color = "lemonchiffon")

```

### Total Countries

```{r}
# Show total countries
valueBox(value = nrow(v_country), icon = "fa-map-location",
         caption = "Countries", color = "lightblue")

```

### Top Country

```{r}
# Show top country
valueBox(value = getmode(v_total$Country), caption = "Top Country", color = "gold")

```

# Description {.sidebar}

The INTIS (INTENT Insights) dashboard provides data visualization of the distribution of contributing artists according to their countries of origin. If you click on a country's outline, you will be able to see information about artists from that country who have contributed, as well as the total number of contributions from the country. The totals for contributions, artists, countries, and mode for countries (top country) are provided as well. The presence of international collaborations results in a slightly higher number of contributions than the total number of tracks; for example, one track featuring two artists from different countries counts as two contributions. The data is available for the whole project as well as for the separate instalments.

# INTENT 2020 {data-navmenu="Instalments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2020)

```{r}
# Prepare data for overview
v_artists20 <- v2020_artists %>%
  unique() %>%
  sort()
v_total20 <- rbind(v2020) %>% as.data.frame()
v_country20 <- table(v_total20$Country) %>% as.data.frame()
colnames(v_country20) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries20 <- inner_join(World, v_country20, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries20)) {
  v_t <- v_total20 %>%
    filter(Country == as.character(ContributingCountries20$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries20$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries20) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Row {data-width=180}

### Total Contributions

```{r}
# Show total contributions
valueBox(value = nrow(v_total20), icon = "fa-music",
         caption = "Contributions", color = "darkseagreen")

```

### Total Artists

```{r}
# Show total artists
valueBox(value = nrow(v_artists20 %>% as.data.frame()), icon = "fa-users",
         caption = "Artists", color = "lemonchiffon")

```

### Total Countries

```{r}
# Show total countries
valueBox(value = nrow(v_country20), icon = "fa-map-location",
         caption = "Countries", color = "lightblue")

```

### Top Country

```{r}
# Show top country
valueBox(value = getmode(v_total20$Country), caption = "Top Country", color = "gold")

```

# INTENT 2021 {data-navmenu="Instalments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2021)

```{r}
# Prepare data for overview
v_artists21 <- v2021_artists %>%
  unique() %>%
  sort()
v_total21 <- rbind(v2021) %>% as.data.frame()
v_country21 <- table(v_total21$Country) %>% as.data.frame()
colnames(v_country21) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries21 <- inner_join(World, v_country21, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries21)) {
  v_t <- v_total21 %>%
    filter(Country == as.character(ContributingCountries21$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries21$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries21) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Row {data-width=180}

### Total Contributions

```{r}
# Show total contributions
valueBox(value = nrow(v_total21), icon = "fa-music",
         caption = "Contributions", color = "darkseagreen")

```

### Total Artists

```{r}
# Show total artists
valueBox(value = nrow(v_artists21 %>% as.data.frame()), icon = "fa-users",
         caption = "Artists", color = "lemonchiffon")

```

### Total Countries

```{r}
# Show total countries
valueBox(value = nrow(v_country21), icon = "fa-map-location",
         caption = "Countries", color = "lightblue")

```

### Top Country

```{r}
# Show top country
valueBox(value = getmode(v_total21$Country), caption = "Top Country", color = "gold")

```

# INTENT 2022 {data-navmenu="Instalments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2022)

```{r}
# Prepare data for overview
v_artists22 <- v2022_artists %>%
  unique() %>%
  sort()
v_total22 <- rbind(v2022) %>% as.data.frame()
v_country22 <- table(v_total22$Country) %>% as.data.frame()
colnames(v_country22) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries22 <- inner_join(World, v_country22, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries22)) {
  v_t <- v_total22 %>%
    filter(Country == as.character(ContributingCountries22$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries22$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries22) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Row {data-width=180}

### Total Contributions

```{r}
# Show total contributions
valueBox(value = nrow(v_total22), icon = "fa-music",
         caption = "Contributions", color = "darkseagreen")

```

### Total Artists

```{r}
# Show total artists
valueBox(value = nrow(v_artists22 %>% as.data.frame()), icon = "fa-users",
         caption = "Artists", color = "lemonchiffon")

```

### Total Countries

```{r}
# Show total countries
valueBox(value = nrow(v_country22), icon = "fa-map-location",
         caption = "Countries", color = "lightblue")

```

### Top Country

```{r}
# Show top country
valueBox(value = getmode(v_total22$Country), caption = "Top Country", color = "gold")

```

# INTENT 2023 {data-navmenu="Instalments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2023)

```{r}
# Prepare data for overview
v_artists23 <- v2023_artists %>%
  unique() %>%
  sort()
v_total23 <- rbind(v2023) %>% as.data.frame()
v_country23 <- table(v_total23$Country) %>% as.data.frame()
colnames(v_country23) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries23 <- inner_join(World, v_country23, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries23)) {
  v_t <- v_total23 %>%
    filter(Country == as.character(ContributingCountries23$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries23$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries23) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Row {data-width=180}

### Total Contributions

```{r}
# Show total contributions
valueBox(value = nrow(v_total23), icon = "fa-music",
         caption = "Contributions", color = "darkseagreen")

```

### Total Artists

```{r}
# Show total artists
valueBox(value = nrow(v_artists23 %>% as.data.frame()), icon = "fa-users",
         caption = "Artists", color = "lemonchiffon")

```

### Total Countries

```{r}
# Show total countries
valueBox(value = nrow(v_country23), icon = "fa-map-location",
         caption = "Countries", color = "lightblue")

```

### Top Country

```{r}
# Show top country
valueBox(value = getmode(v_total23$Country), caption = "Top Country", color = "gold")

```
